\documentclass{article}
\usepackage{fancyhdr}
\usepackage{datetime}
\usepackage{parskip}
\usepackage{graphicx}

\newdateformat{monthyeardate}{\monthname[\THEMONTH], \THEYEAR}

\pagestyle{fancy}

\fancyhf{}
\fancyfoot[L]{University of Oulu. \monthyeardate\today}

\lhead{IoT Data Analytics}
\rhead{Page \thepage}

\title{
Exercise 2: IoT Data Analytics
\bigskip
\author{Andrei Golubev 2621924 \\ Hassan Shaheen 2600602}
\date{\parbox{\linewidth}{\centering
  \endgraf\bigskip
  University of Oulu, Oulu, Finland
  \endgraf\monthyeardate\today}}
}

\setlength{\parindent}{0pt}

\begin{document}
\maketitle
\thispagestyle{empty}
\newpage

\section{Visualization}

Visualization implementation can be divided into two separate tasks: data preparation and actual
implementation. The first one is required when the data is not ready for the use (e.g. collected
from different sources or in a wrong format), which is usually the case in real world data
visualization. The second relies on the use case and research topic and should ideally simplify data
analysis. In the following subsections we describe briefly the visualization approach details.

\subsection{Data preparation}

There are two primary data files that need to be considered: sensor measurements (temperature, pir,
co2, etc.) and sensor GPS coordinates.

We perform the following preprocessing on the \textbf{Sensor GPS coordinates} file:

* Move out all unnecessary information (e.g. Tellus area GPS coordinates).

* Convert XLSX format file into plain CSV.

* Unify device id format between this file and sensor measurements file.

* Convert GPS coordinates into relative to Tellus area coordinates (this is a necessary step for
futher visualization and explained below).

\textbf{Sensor measurements} file is also preprocessed:

* Only required information is left: device ids (required for later localization), timestamps, pir
readings.

* The whole data file is split into \textit{monthly} data (a single CSV contains 1 month of sensor
measurements). In our use case, monthly separation is sufficient and the benefits of such a split
are not to be ignored as we gain reduced the memory footprint during visualization and as well as
significant speed up during parsing.

With the described actions in mind, we are able to successfully implement visualization that gives
us a good base for future analysis.

\subsection{Visualization implementation}

\section{Seasonal variations}

\section{Future implications}


\end{document}
